\documentclass[11pt,article,oneside]{memoir}
\usepackage[left=2cm, right=2cm, top=2cm]{geometry}

\setsecheadstyle{\Large\scshape}
\setsubsecheadstyle{\large\scshape\hspace{5mm}}

\begin{document}

\title{\LARGE Life Science}
\author{\Large Mr. Braunberger \newline \\ \footnotesize\texttt{\noindent jacob.braunberger@k12.nd.us}}
\date{\hspace*{2.3cm}Fall 2018 \newline \noindent \hspace*{-1.5cm} 8:25am--9:15am}

\setlength{\epigraphwidth}{.8\textwidth}

\maketitle

\epigraph{I think it is very important--at least it was to me--that if you are going to teach people to make observations, you should show that something wonderful can come from them.}{\textit{--Richard Feynman}}




\section*{Course Description}
Life science is the natural science that studies life and living organisms, including their physical structure, chemical processes, molecular interactions, physiological mechanisms, development and evolution. Despite the complexity of the science, there are certain unifying concepts that consolidate it into a single, coherent field.\footnote{Wikipedia} Upon successful completion of this course, the student will, among other things, have
developed critical thinking skills and be knowledgeable in the field.


\section*{Procedures, Materials, and Expectations}
\subsection*{Materials}
	Everyday, the student is expected to bring to class their textbook, a pencil or pen, and a notebook. The student is responsible
for the textbook issued to them and any damage it incurs.
\subsection*{Expectations}
	Science is a subject that builds upon itself and therefore requires study on a daily basis.
    Assignments issued is to be turned in on time. Late work will be accepted; however,
late assignments will be automatically docked 30\%. Assignments may be completed in pen or pencil, as long as the assignment is neat.
Phones are to be turned on silent and kept in the area specified by the instructor. Violation of this policy will result in detention.


The course will model scientific thought: errors are to be expected, discovered, and remedied. Any incorrect answers
on homework will be awarded 50\% credit if recompleted correctly within a week of receiving the homework.

\subsection*{Grading}
	Tests and quizzes will be worth 15\% of the grade. The final will be worth 20\% of the grade. Homework will be worth 65\% of the grade.


\section*{Supplementary Resources}
Supplementary resources will be disseminated as necessary.